Optifcal Observations of an Extraordinarily Young Type Ia Supernova iPTF16abc

### 2017-06-06 doc/ms.tex

We determine the time of rest-frame \textit{B}-band maximum to be 
 $\textrm{MJD}_{max}=57499.54\pm0.23$, the coefficient
of the zeroth principle component $x_0 = XXX \pm XXX$, the
coefficient of the first principle component $x_1 = 0.9655 \pm 0.0003$, and
the color term $c = 0.012 \pm 0.029$. The best-fit model also gives an
unreddened apparent peak magnitude of $m^*_{B}=15.6\,\textrm{mag}$ \ycao{uncertainties on Bmax?} in
the SN rest frame.

>>>>

We determine the time of rest-frame \textit{B}-band maximum to be 
 $\textrm{MJD}_{max}=57499.54\pm0.23$, the coefficient
of the zeroth principle component $x_0 = 0.0093 \pm 0.0003$, the
coefficient of the first principle component $x_1 = 0.97 \pm 0.15$, and
the color term $c = 0.012 \pm 0.029$. The best-fit model also gives an
unreddened apparent peak magnitude of $m^*_{B}=15.6\,\textrm{mag}$ \ycao{uncertainties on Bmax?} in
the SN rest frame.
